Visualize ukb whole genome, s40.22

### 2020-10-31 analysis/simulation-susieI-ukbWG-gtex.adipose_visual.Rmd
logBF

  a[, "PVALUE"] <- -log10(a[, "pvalue"])

@@

  fig1 <- plot_susie_pip(dt.gene) 
  #fig2 <- plot_beta(dt.gene)
  fig3 <- plot_p(dt.gene)

  fig4 <- plot_susie_pip(dt.snp)
  #fig5 <- plot_beta(dt.snp) 
  fig6 <- plot_p(dt.snp) %>% layout( plot_bgcolor='#EFF6FC')

  # fig <- subplot(fig1, fig2, fig3, fig4, fig5, fig6, nrows=6, shareX = T, titleY = T)

  fig <- subplot(fig1, fig3, fig4, fig6, nrows=4, shareX = T, titleY = T)

  fig <- fig %>% layout(autosize = F, width = 600, height = 600, margin = 0.02,
                        xaxis = list(title = "Genomic position"))

@@

first two rows are for genes, last two rows are for SNPs.

>>>>

  a[, "PVALUE"] <- -log10(a[, "pvalue"])
  a[, "lbf"] <- log10(exp(a[, "lbf"]))

@@

  fig1 <- plot_susie_pip(dt.gene) 
  fig2 <- plot_lbf(dt.gene)
  fig3 <- plot_p(dt.gene)

  fig4 <- plot_susie_pip(dt.snp)
  fig5 <- plot_lbf(dt.snp) 
  fig6 <- plot_p(dt.snp) %>% layout( plot_bgcolor='#EFF6FC')

  fig <- subplot(fig1, fig2, fig3, fig4, fig5, fig6, nrows=6, shareX = T, titleY = T)

  fig <- fig %>% layout(autosize = F, width = 600, height = 800, margin = 0.02,
                        xaxis = list(title = "Genomic position"))

@@

First three rows are for genes, last three rows are for SNPs.
